---
title: Playing with D3
author: ~
date: '2021-07-20'
slug: playing-with-d3
categories: []
tags: []
---

I wanted to try out using `D3` in an R Markdown document, to see how it works. Using `r2d3`, it works really well! 

Me and [Mandy Norrbo](https://twitter.com/MandyNorrbo) were messing around trying to make some purely fun stuff in `D3`, which you don't really see too much. And this is what I made. I would usually go for `p5.js` to make stuff like this, but it was a nice challenge to do it in `D3` instead.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(r2d3)
```

# The Cucumber

Chop the cucumber! (hover your mouse over the circles)
```{r}
r2d3(data=sin(seq(0, 2, 0.03)), script = "js/cucumber.js")
```

# Animated cucumber

Watch the cucumber chop itself! (Alert: this is not a GIF, the slices are jumping to random places each time)

```{r}
r2d3(data=sin(seq(0, 2, 0.03)), script = "js/cucumberAnimated.js")
```

# The Worm

The worm will jump out the way of your mouse

```{r}
r2d3(data=seq(1, 100, 5), height = 200, script = "js/worm.js")
```

# Flowing pink sun

A pink blob will follow your mouse!

```{r}
r2d3(data=seq(1, 100, 5), script = "js/cursor.js")
```

See the code on [GitHub](https://github.com/daikman/playing_with_d3).






